Pathogen Spillover - dissertation chapter

### 2018-10-10 pathogen-spillover-diss-ch.Rmd
Add figure of significant relationships in path model.

---
title: "Pathogen Spillover - dissertation chapter"
author: "Whalen Dillon"
date: "`r Sys.Date()"
output:
  html_document:
    self_contained: no
    toc: true
    toc_float: true
  pdf_document: default
  word_document: default
---

@@

plot_model(shannon.mod, type = "slope", show.values = T)
plot_model(shannon.mod, type = "std", show.values = T, 
           title = "Standardized coefficient estimate")
S.plot <- plot_model(shannon.mod, type = "slope")

@@

(shannon.plot <- ggplot(oaks.data, aes(twi15m, h2005)) +
      geom_point(alpha = .7) +
      # geom_smooth(method = "loess", se = F, color = "gray50", linetype = "dashed") +
      geom_smooth(method = "lm", color = "black") +
      theme_classic() +
      xlab("Topographic index") +
      ylab("Tree diversity (H')") +
      theme(strip.background = element_blank(),
            strip.text = element_blank()) +
      NULL
      )

@@

# effect plots
plot_model(lfct.mod, type = "slope") +
      theme_bw() +
      ylab("log (leaf count + 1)") +
      theme(strip.background = element_blank()) +
      NULL

plot_model(lfct.mod, type = "pred", terms = c("hrs25", "tot_bay.ln1")) +
      theme_classic() +
      ylab("log( leaf count + 1 )") +
      xlab("Hours >25 ºC") +
      ggtitle("Predicted values") +
      NULL

slc_vs_bay_plot <- ggplot(oaks.data, aes(tot_bay.ln1, lfct)) +
      geom_point(alpha = .7) +
      geom_smooth(method = "lm", color = "black") +
      xlab("log( Bay laurel count )") +
      ylab("log( Symptomatic leaf count )") +
      theme_classic()
slc_vs_hrs25_plot <- ggplot(oaks.data, aes(hrs25, lfct)) +
      geom_point(alpha = .7) +
      geom_smooth(method = "lm", color = "black") +
      xlab("Number of hours >25 ºC") +
      ylab("log( Symptomatic leaf count )") +
      theme_classic()

cowplot::plot_grid(slc_vs_bay_plot, slc_vs_hrs25_plot, nrow = 2)

@@

@@

ggplot(oaks.data, aes(twi15m, hrs25)) +
      geom_point(alpha = .3) +
      geom_smooth(method = "lm", color = "black") +
      xlab("Topographic index") +
      ylab("Number of hours >25 ºC") +
      theme_classic()

@@

cowplot::plot_grid(
      plot_model(inf.mod, type = "est", show.values = T, 
                 title = "Oak infection coefficient estimates") +
            # geom_hline(yintercept = 1, color = "gray80",linetype = "dashed") +
            theme_classic(),
      plot_model(inf.mod, type = "std", show.values = T, 
                 title = "Oak infection std. coefficient estimates",
                 # vline.color = "gray80"
                 ) +
            theme_classic(),
      nrow = 2
      )

plot_model(inf.mod, type = "pred", terms = c("lfct"), show.data = T) +
      # geom_point() +
      theme_classic() +
      xlab("log( symptomatic leaf count + 1 )") +
      ylab("Predicted probability for oak infection") +
      ggtitle("") +
      NULL

ggplot(oaks.data, aes(exp(lfct), inf_oak_ct/(inf_oak_ct+uninf_oak_ct))) +
      # geom_point(alpha = .5) +
      stat_sum() +
      facet_grid(year~.) +
      geom_smooth(method = "loess", color = "black") +
      theme_classic() +
      NULL

@@

>>>>

---
title: "Pathogen Spillover - dissertation chapter"
author: "Whalen Dillon"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: no
    toc: true
    toc_float: true
  pdf_document: default
  word_document: default
---

@@

plot_model(shannon.mod, type = "slope", show.values = T)
plot_model(shannon.mod, type = "std", show.values = T, 
           title = "Standardized coefficient estimate")
S.plot <- plot_model(shannon.mod, type = "pred", terms = "twi15m")

@@

(shannon.plot <- plot_model(shannon.mod, type = "pred", terms = "twi15m") +
      geom_point(data = oaks.data, 
                 aes(twi15m, h2005), 
                 alpha = .1, size = 1, position = "jitter") +
      # geom_smooth(method = "loess", se = F, color = "gray50", linetype = "dashed") +
      # geom_smooth(method = "lm", color = "black") +
      theme_classic() +
      xlab("Topographic index") +
      ylab("Tree diversity (H')") +
      theme(strip.background = element_blank(),
            strip.text = element_blank()) +
      NULL
      )

@@

# effect plots
plot_model(lfct.mod, type = "slope", show.data = T, colors = "blambus") +
      # geom_point(color = "black", alpha = .1) +
      # geom_smooth(method = "lm", color = "black", fill = "black") +
      # geom_smooth(method = "loess", color = NA) +
      theme_bw() +
      ylab("log (leaf count + 1)") +
      # theme(strip.text = element_blank()) +
      NULL

slc_vs_bay_plot <- plot_model(lfct.mod, type = "pred", terms = c("tot_bay.ln1"), show.data = F) +
      geom_point(data = oaks.data, aes(x = tot_bay.ln1, y = lfct),alpha = .1, size = 1) +
      theme_classic() +
      ylab("Symptomatic leaf count") +
      xlab("Bay laurel density") +
      ggtitle("Model fit") +
      NULL

slc_vs_hrs25_plot <- plot_model(lfct.mod, type = "pred", terms = c("hrs25"), show.data = F) +
      geom_point(data = oaks.data, 
                 aes(x = hrs25, y = lfct),
                 alpha = .1, size = 1) +
      theme_classic() +
      ylab("Symptomatic leaf count") +
      xlab("Hours >25 ºC") +
      ggtitle("Model fit") +
      NULL

# ggeffects::ggpredict(lfct.mod)

# slc_vs_bay_plot <- ggplot(oaks.data, aes(tot_bay.ln1, lfct)) +
#       geom_point(alpha = .7) +
#       geom_smooth(method = "lm", color = "black") +
#       xlab("log( Bay laurel count )") +
#       ylab("log( Symptomatic leaf count )") +
#       theme_classic()
# 
# slc_vs_hrs25_plot <- ggplot(oaks.data, aes(hrs25, lfct)) +
#       geom_point(alpha = .7) +
#       geom_smooth(method = "lm", color = "black") +
#       xlab("Number of hours >25 ºC") +
#       ylab("log( Symptomatic leaf count )") +
#       theme_classic()

cowplot::plot_grid(slc_vs_bay_plot, 
                   slc_vs_hrs25_plot,
                   labels = "auto",
                   nrow = 2)

@@

# ggplot(oaks.data, aes(tot_bay, tot_lfct)) +
#       geom_point() +
#       scale_x_log10() +
#       scale_y_log10()

@@

# Fitted line with the observed data.
hot.mod.plot <- plot_model(hot.mod, type = "pred", terms = "twi15m", show.data = F) +
      geom_point(data = oaks.data, 
                         aes(x = twi15m, y = hrs25),
                         alpha = .1) +
      theme_classic() +
      ylab("Number of hours >25 ºC") +
      xlab("Topographic index") +
      theme(strip.background = element_blank(),
            strip.text = element_blank()) +
      NULL

(hot.mod.plot2 <- ggplot(oaks.data, 
                         aes(twi15m, hrs25,
                             # color = as.factor(year)
                             )
                         ) +
      geom_point(alpha = .1) +
      # geom_smooth(method = "lm", se = F) +
      geom_smooth(method = "lm", se = T, color = "black") +
      scale_color_viridis_d() +
      xlab("Topographic index") +
      ylab("Number of hours >25 ºC") +
      theme_classic() +
      NULL
      )

@@

cowplot::plot_grid(
      plot_model(inf.mod, type = "est", show.values = T, 
                 title = "Oak infection coefficient estimates",
                 vline.color = "gray80") +
            # geom_hline(yintercept = 1, color = "gray80",linetype = "dashed") +
            theme_classic(),
      plot_model(inf.mod, type = "std", show.values = T, 
                 title = "Oak infection std. coefficient estimates",
                 vline.color = "gray80"
                 ) +
            theme_classic(),
      nrow = 2
      )

inf.lfct.plot <- plot_model(inf.mod, type = "pred", terms = c("lfct"), show.data = T) +
      # geom_point() +
      theme_classic() +
      xlab("Symptomatic leaf count") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL

# marginal effects of each significant predictor variable
cowplot::plot_grid(
inf.lfct.plot <- inf.lfct.plot +
      geom_point(data = oaks.data, 
                 aes(x = lfct, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1),
# inf.lfct.plot +
#       geom_point(data = filter(oaks.data, inf_oak_ct/(inf_oak_ct+uninf_oak_ct) <.5), 
#                  aes(x = lfct, 
#                      y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
#                      ),
#                  alpha = .4, size = 1),

inf.h2005.plot <- plot_model(inf.mod, type = "pred", terms = c("h2005"), show.data = T) +
      geom_point(data = oaks.data, 
                 aes(x = h2005, 
                     y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)
                     ),
                 alpha = .1, size = 1) +
      theme_classic() +
      xlab("Shannon's diversity index") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL,

inf.hrs1422.plot <- plot_model(inf.mod, type = "pred", terms = c("hrs1422")) +
      geom_point(data = oaks.data, aes(x = hrs1422, y = inf_oak_ct/(inf_oak_ct+uninf_oak_ct)), alpha = .1, size = 1) +
      theme_classic() +
      xlab("Hours 14-22 ºC") +
      ylab("Infected oaks (%)") +
      ggtitle("") +
      NULL,
labels = "auto"
)

ggplot(oaks.data, aes((lfct), inf_oak_ct/(inf_oak_ct+uninf_oak_ct), color = as.factor(year))) +
      geom_point(alpha = .5) +
      # geom_line(aes(x=lfct, y=predict(inf.mod))) +
      geom_smooth(aes(y=predict(inf.mod, type = "response")), method = "gam", formula = y~s(x, bs="cs"), se=F) +
      scale_color_viridis_d() +
      # stat_sum() +
      # facet_grid(year~.) +
      # geom_smooth(method = "loess", color = "black") +
      theme_classic() +
      NULL
# 
# 
# inf.pred <- ggeffects::ggpredict(inf.mod, full.data = T)
# 
# ggplot(inf.pred$lfct, aes(x, predicted)) +
#       # geom_point(data = oaks.data, aes(x = lfct, y = )) +
#       geom_path()
#       
# inf.pred$h2005
# 
# inf.mod.predict <- predict(inf.mod)

@@

# Combine significant relationships from fitted models

```{r significant relationships figure}

cowplot::plot_grid(
      inf.lfct.plot,
      inf.h2005.plot +
            xlab("Tree diversity (H')"),
      inf.hrs1422.plot,
      slc_vs_bay_plot +
            ggtitle(""),
      slc_vs_hrs25_plot +
            ggtitle(""),
      shannon.plot +
            ggtitle(""),
      hot.mod.plot +
            ggtitle(""),
      labels = "auto", label_x = .01
      )
